Ant cuticle image classification using texture analysis: a comparative study

### 2022-07-10 paper/main.tex
figures and tables update

We examine ants (\textit{Formicidae}) as they display an extreme diversity of
cuticle micro sculpturing across all subfamilies. Sculpturing ranges from
parallel longitudinal ridges to deep oval impressions to erratic protuberances.
The sculpturing has arisen convergently and independently throughout ant's
evolutionary history, which suggests some inherent function. Cuticle sculpturing
on ants may help increase strength and rigidness, resist abrasion, increase
internal and external surface area, resist microbial growth, and rear beneficial
anti-biotic producing bacteria \cite{johnson_effect_2011,
    bruckner_relationship_2017, currie_coevolved_2006}. These specific functions may
be associated with certain sculpturing types. In order to analyze those
functions, it is necessary to segment the image and group similar textures for
further analysis.

@@

\subsection{Sculpturing identification}
Taxonomists have developed extensive terminology describing ant cuticle
sculpturing as it is often a useful diagnostic trait to distinguish between
closely related ant species \cite{blaimer_taxonomy_2019,fisher_ants_2007}. The
definitive text on ant cuticle terminology — \textit{The Glossary of Surface
    Sculpturing} — contains over 100 terms to describe the cuticle sculpturing
patterns of ants \cite{harris_glossary_1979}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{thesis_assets/images/rough_collage.png}
    \caption{Examples of rough cuticle texture ant images in the dataset after
        center cropping, from AntWeb \cite{perrichot_antweb_2012}.}
    \label{fig:rough-cuticle-texture}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{thesis_assets/images/smooth_collage.png}
    \caption{Examples of smooth cuticle texture ant images in the dataset after
        center cropping, from AntWeb \cite{perrichot_antweb_2012}.}
    \label{fig:smooth-cuticle-texture}
\end{figure}

@@

Initially, the sculpture identification protocol had 8 subcategories of cuticle
texture, including dimpled, ridged, and differing levels of smooth texture. For
simplicity, we work only with the two main categories. The training set
identifications were reviewed together as a group by the assistants. Once
training was complete, assistants were assigned the same genera of ants to
identify independently each week. A weekly meeting was held to discuss
identifications and assign new ones. These identifications were collected in the
master spreadsheet and the identifications were assigned to individual ant
species on a majority basis.

@@

Due to the variety of the ant head image attributes, we apply simple
preprocessing before the images are used in our model. We want the images to
have a uniform size for simplicity in our classification process. Since the ant
head images are typically centered in the image, we apply a center crop to each
image to create a square image of the same size. Once the image is square, we
resize each image to a fixed size of 256x256 pixels. We leave other
discrepancies in the images untouched.

@@

For the feasibility study in this ant image datasets, we use both K-means and
K-views in our experiments as both are statistical clustering methods. The
experiments may indicate how well the statistical approach will do in this type
of textural images. In pre-processing the dataset, we apply the Gabor filter to
transform the gray-scale ant image into four Gabor-filtered channels, subtract
the gray-scale image from each channel, take the absolute value of the resulting
images, and then normalize them. This pre-processing will highlight some of
characteristics features such as edge-like in the image. This step is very
useful in feeding the datasets to the K-views algorithms. A 10-channel Gabor
filter is applied in the pre-processing step for the K-means algorithm.

@@

To begin, we share the results on the each algorithm specified in the
methodology section using the evaluation metrics described. The results are
shown in Table \ref{tab:results}. It should be noted that due to the class
imbalance in the dataset, the F1 score is the preferable metric to the accuracy.
Therefore, the results have been sorted by F1 score in descending order.

\begin{table}[h]
    \centering
    \caption{Results}
    \input{assets/results.tex}
    \label{tab:results}
\end{table}

@@

@@

In this section, we provide some visual analysis of some correctly and
incorrectly classified images using GradCAM. We provide two categories and two
subcategories in our analysis. The two categories are correct and incorrect
classification. Regardless of the feature activation map, the correctly
classified images have the same predicted label as the ground truth, and
incorrectly classified images have different predicted labels. The two
subcategories are expected and non-expected feature activation. In the expected
case, the features that are used to compute the classification are the same as
the features used by the assistants in the sculpture identification process. In
general, the features used by the assistants are the textures of the cuticle on
the ant head. In the non-expected case, the features used to compute the
classification are not from the head, for example, from the background,
extraneous text, or the body of the ant. We used randomly selected images from
the dataset and the fine-tuned ResNet101 model to perform the analysis. We show
the GradCAM results in Figures \ref{fig:correct_ideal},
\ref{fig:correct_nonideal}, \ref{fig:incorrect_ideal}, and
\ref{fig:incorrect_nonideal}. The left image shows the preprocessed image input
to the model. The right image shows the GradCAM output based on the
classification. Four specimens were selected randomly from each category and
subcategory.

Correctly classified images which use the expected features show the ideal
performance of the model. Incorrectly classified images which use the expected
features should be further analyzed. In essence, the model in this situation
knows \textit{where} to look, but not \textit{what} to look for. In Figure
\ref{fig:incorrect_ideal_84}, the features activated are mostly in the correct
location on the ant head, and the rough texture is clearly visible, yet the
model predicts the incorrect class \textit{smooth}. Similarly in Figure
\ref{fig:incorrect_ideal_177}, the features activated are also mostly in the
correct location, yet the model predicts the incorrect class \textit{smooth}. In
this case, it may be due to the pose of the ant being slightly different from
the average pose. In the incorrectly classified images with non-expected
features, analysis shows that the model is unable to find \textit{where} to
look, and obtains feature information from other parts of the ant or the
background. Cases where the image was correctly classified using the
non-expected features can basically be seen as noise. In order to further
analyze this class, we should introduce some parameter such as model confidence
to examine further.

\newcommand{\subwidth}{0.35\textwidth}
\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/518.png}
        \caption{Ground truth: smooth}
        \label{fig:correct_ideal_518}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/808.png}
        \caption{Ground truth: smooth}
        \label{fig:correct_ideal_808}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/842.png}
        \caption{Ground truth: rough}
        \label{fig:correct_ideal_842}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/1091.png}
        \caption{Ground truth: rough}
        \label{fig:correct_ideal_1091}
    \end{subfigure}
    \caption{Correctly classified images using expected features.}
    \label{fig:correct_ideal}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/346.png}
        \caption{Ground truth: rough}
        \label{fig:correct_nonideal_346}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1554.png}
        \caption{Ground truth: rough}
        \label{fig:correct_nonideal_1554}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1694.png}
        \caption{Ground truth: rough}
        \label{fig:correct_nonideal_1694}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/388.png}
        \caption{Ground truth: smooth}
        \label{fig:correct_nonideal_388}
    \end{subfigure}
    \caption{Correctly classified images using non-expected features.}
    \label{fig:correct_nonideal}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/84.png}
        \caption{Ground truth: rough}
        \label{fig:incorrect_ideal_84}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/86.png}
        \caption{Ground truth: smooth}
        \label{fig:incorrect_ideal_86}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/177.png}
        \caption{Ground truth: smooth}
        \label{fig:incorrect_ideal_177}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/197.png}
        \caption{Ground truth: smooth}
        \label{fig:incorrect_ideal_197}
    \end{subfigure}
    \caption{Incorrectly classified images using expected features.}
    \label{fig:incorrect_ideal}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/1.png}
        \caption{Ground truth: rough}
        \label{fig:incorrect_nonideal_1}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/22.png}
        \caption{Ground truth: rough}
        \label{fig:incorrect_nonideal_22}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/61.png}
        \caption{Ground truth: rough}
        \label{fig:incorrect_nonideal_61}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/204.png}
        \caption{Ground truth: rough}
        \label{fig:incorrect_nonideal_204}
    \end{subfigure}
    \caption{Incorrectly classified images using non-expected features.}
    \label{fig:incorrect_nonideal}
\end{figure}

>>>>

We examine ants (\textit{Formicidae}) as they display an extreme diversity of
cuticle micro sculpturing across all subfamilies. Microsculpture ranges from
parallel longitudinal ridges to deep oval impressions to erratic protuberances.
Microsculpture has arisen convergently and independently throughout ant's
evolutionary history, which suggests  that these are complex traits undergoing
selection. Cuticle microsculpture on ants may help increase strength and
rigidness, resist abrasion, increase internal and external surface area, resist
microbial growth, and rear beneficial anti-biotic producing bacteria
\cite{johnson_effect_2011, bruckner_relationship_2017, currie_coevolved_2006}.
These specific functions may be associated with certain sculpturing types. In
order to analyze those functions, it is necessary to segment the image and group
similar textures for further analysis.

@@

\subsection{Microsculpture identification}
Taxonomists have developed extensive terminology describing ant cuticle
microsculpture as it is often a useful diagnostic trait to distinguish between
closely related ant species \cite{blaimer_taxonomy_2019,fisher_ants_2007}. The
definitive text on ant cuticle terminology — \textit{The Glossary of Surface
    Sculpturing} — contains over 100 terms to describe the cuticle sculpturing
patterns of ants \cite{harris_glossary_1979}. Despite the numerous ways to
describe microsculpture, in general, microsculpture diversity falls into two
classes - smooth and rough. Smooth ants are free of any obvious microsculpture
and may have small hairs that give the cuticle a dull appearance. Rough ants
have a variety of raised lines or depressed textures on the cuticle. The
entirety of ant microsculpture is represented within these two classes.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{assets/images/rough_full_collage.png}
    \caption{Examples of rough cuticle texture ant images in the dataset after
        center cropping, from AntWeb \cite{perrichot_antweb_2012}.}
    \label{fig:rough-cuticle-texture}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{assets/images/smooth_full_collage.png}
    \caption{Examples of smooth cuticle texture ant images in the dataset after
        center cropping, from AntWeb \cite{perrichot_antweb_2012}.}
    \label{fig:smooth-cuticle-texture}
\end{figure}

@@

Initially, the sculpture identification protocol had 5 subcategories of cuticle
texture: smooth, punctate, striate, reticulate, and tuberous. For simplicity, we
work only with the two main categories. The training set identifications were
reviewed together as a group by the assistants. Once training was complete,
assistants were assigned the same genera of ants to identify independently each
week. A weekly meeting was held to discuss identifications and assign new ones.
These identifications were collected in the master spreadsheet and the
identifications were assigned to individual ant species on a majority basis.

@@

Due to the variety of the ant head image attributes, we apply simple
preprocessing before the images are used in our model. We want the images to
have a uniform size for simplicity in our classification process. Since the ant
head images are typically centered in the image, we apply a center crop to each
image to create a square image of the same size. Once the image is square, we
resize each image to a fixed size of 256x256 pixels. We leave other
discrepancies in the images untouched. A summary of the resulting dataset is
shared in Table \ref{tab:dataset-summary}.

\begin{table}[h]
    \centering
    \caption{Summary of the dataset.}
    \begin{tabular}{lc}
        \toprule
        Total images  & 2499    \\
        Rough images  & 1072    \\
        Smooth images & 1427    \\
        Image size    & 256x256 \\
    \end{tabular}
    \label{tab:dataset-summary}
\end{table}

@@

For the feasibility study in this ant image datasets, we use both K-means and
K-views in our experiments as both are statistical clustering methods. The
experiments may indicate how well the statistical approach will do in this type
of textural images. In pre-processing the dataset, we apply the Gabor filter to
transform the gray-scale ant image into four Gabor-filtered channels, subtract
the gray-scale image from each channel, take the absolute value of the resulting
images, and then normalize them. This pre-processing will highlight some of
characteristics features such as edge-like in the image. This step is very
useful in feeding the datasets to the K-views algorithms. A 10-channel Gabor
filter is applied in the pre-processing step for the K-means algorithm. The
theta $\theta$ parameters in the Gabor filters used are multiples of $\pi/10$
radians starting from $0$ to $\pi$ radians. The Gabor filter lambda $\lambda$
parameter is equal to $\pi$.

@@

To begin, we share the results on the each algorithm specified in the
methodology section using the evaluation metrics described. The results are
shown in Table \ref{tab:results}. It should be noted that due to the class
imbalance in the dataset, the F1 score is the preferable metric to the accuracy.
% Therefore, the results have been sorted by F1 score in descending order.

\begin{table}[h]
    \centering
    \caption{Experimental results of different algorithms}
    \input{assets/results.tex}
    \label{tab:results}
\end{table}

@@

% \subsection{Clustering segmentation}

@@

In this section, we provide some visual analysis of some correctly and
incorrectly classified images using GradCAM. We provide two categories and two
subcategories in our analysis. The two categories are correct and incorrect
classification. Regardless of the feature activation map, the correctly
classified images have the same predicted label as the ground truth, and
incorrectly classified images have different predicted labels. The two
subcategories are expected and non-expected feature activation. In the expected
case, the features that are used to compute the classification are the same as
the features used by the assistants in the sculpture identification process. In
general, the features used by the assistants are the textures of the cuticle on
the ant head. In the non-expected case, the features used to compute the
classification are not from the head, for example, from the background,
extraneous text, or the body of the ant. We used randomly selected images from
the dataset and the fine-tuned ResNet101 model to perform the analysis. We show
the GradCAM results in Figures \ref{fig:correct_images} and
\ref{fig:incorrect_images}. The left image shows the preprocessed image input
to the model. The right image shows the GradCAM output based on the
classification. Four specimens were selected randomly from each category and
subcategory.

Correctly classified images which use the expected features show the ideal
performance of the model. Incorrectly classified images which use the expected
features should be further analyzed. In essence, the model in this situation
knows \textit{where} to look, but not \textit{what} to look for. In Figure
\ref{fig:incorrect_images}, there are results where the features activated are
mostly in the correct location on the ant head, and the rough texture is clearly
visible, yet the model predicts the incorrect class \textit{smooth}. Similarly
in Figure \ref{fig:incorrect_images}, there are results where the features
activated are also mostly in the correct location, yet the model predicts the
incorrect class \textit{smooth}. In this case, it may be due to the pose of the
ant being slightly different from the average pose. In the incorrectly
classified images with non-expected features, analysis shows that the model is
unable to find \textit{where} to look, and obtains feature information from
other parts of the ant or the background. Cases where the image was correctly
classified using the non-expected features can basically be seen as noise. In
order to further analyze this class, we should introduce some parameter such as
model confidence to examine further.

\newcommand{\subwidth}{0.35\textwidth}
% \begin{figure}
%     \centering
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/518.png}
%         \caption*{Smooth texture}
%         \label{fig:correct_ideal_518}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/808.png}
%         \caption*{Smooth texture}
%         \label{fig:correct_ideal_808}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/842.png}
%         \caption*{Rough texture}
%         \label{fig:correct_ideal_842}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/1091.png}
%         \caption*{Rough texture}
%         \label{fig:correct_ideal_1091}
%     \end{subfigure}
%     \caption{Correctly classified images using expected features.}
%     \label{fig:correct_ideal}
% \end{figure}

% \begin{figure}
%     \centering
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/346.png}
%         \caption*{Rough texture}
%         \label{fig:correct_nonideal_346}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1554.png}
%         \caption*{Rough texture}
%         \label{fig:correct_nonideal_1554}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1694.png}
%         \caption*{Rough texture}
%         \label{fig:correct_nonideal_1694}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/388.png}
%         \caption*{Smooth texture}
%         \label{fig:correct_nonideal_388}
%     \end{subfigure}
%     \caption{Correctly classified images using non-expected features.}
%     \label{fig:correct_nonideal}
% \end{figure}

\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/518.png}
        \caption*{Smooth texture}
        \label{fig:correct_ideal_518}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/808.png}
        \caption*{Smooth texture}
        \label{fig:correct_ideal_808}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/842.png}
        \caption*{Rough texture}
        \label{fig:correct_ideal_842}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_ideal/1091.png}
        \caption*{Rough texture}
        \label{fig:correct_ideal_1091}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/346.png}
        \caption*{Rough texture}
        \label{fig:correct_nonideal_346}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1554.png}
        \caption*{Rough texture}
        \label{fig:correct_nonideal_1554}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/1694.png}
        \caption*{Rough texture}
        \label{fig:correct_nonideal_1694}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/correct_nonideal/388.png}
        \caption*{Smooth texture}
        \label{fig:correct_nonideal_388}
    \end{subfigure}
    \caption{Correctly classified images.}
    \label{fig:correct_images}
\end{figure}

% \begin{figure}
%     \centering
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/84.png}
%         \caption*{Rough texture}
%         \label{fig:incorrect_ideal_84}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/86.png}
%         \caption*{Smooth texture}
%         \label{fig:incorrect_ideal_86}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/177.png}
%         \caption*{Smooth texture}
%         \label{fig:incorrect_ideal_177}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/197.png}
%         \caption*{Smooth texture}
%         \label{fig:incorrect_ideal_197}
%     \end{subfigure}
%     \caption{Incorrectly classified images using expected features.}
%     \label{fig:incorrect_ideal}
% \end{figure}

% \begin{figure}
%     \centering
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/1.png}
%         \caption*{Rough texture}
%         \label{fig:incorrect_nonideal_1}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/22.png}
%         \caption*{Rough texture}
%         \label{fig:incorrect_nonideal_22}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/61.png}
%         \caption*{Rough texture}
%         \label{fig:incorrect_nonideal_61}
%     \end{subfigure}
%     \begin{subfigure}{\subwidth}
%         \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/204.png}
%         \caption*{Rough texture}
%         \label{fig:incorrect_nonideal_204}
%     \end{subfigure}
%     \caption{Incorrectly classified images using non-expected features.}
%     \label{fig:incorrect_nonideal}
% \end{figure}

\begin{figure}
    \centering
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/84.png}
        \caption*{Rough texture}
        \label{fig:incorrect_ideal_84}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/86.png}
        \caption*{Smooth texture}
        \label{fig:incorrect_ideal_86}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/177.png}
        \caption*{Smooth texture}
        \label{fig:incorrect_ideal_177}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_ideal/197.png}
        \caption*{Smooth texture}
        \label{fig:incorrect_ideal_197}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/1.png}
        \caption*{Rough texture}
        \label{fig:incorrect_nonideal_1}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/22.png}
        \caption*{Rough texture}
        \label{fig:incorrect_nonideal_22}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/61.png}
        \caption*{Rough texture}
        \label{fig:incorrect_nonideal_61}
    \end{subfigure}
    \begin{subfigure}{\subwidth}
        \includegraphics[width=1\linewidth]{thesis_assets/gradcam/incorrect_nonideal/204.png}
        \caption*{Rough texture}
        \label{fig:incorrect_nonideal_204}
    \end{subfigure}
    \caption{Incorrectly classified images.}
    \label{fig:incorrect_images}
\end{figure}
